On Secure Delegation of SampBQP with a Classical Client

### 2020-02-07 bqp.tex
Make the project compile properly
Make BQP protos more rigorous

\Ethan{More feedback notes go here to be implemented later}

@@

\Ethan{protocol 2 should say 1 message QPIP1 for BQP}

\Ethan{``choose some tensor"? need distribution info and some basis choice}

\Ethan{Try copying from https://arxiv.org/pdf/1911.08101.pdf pg 11?}

\Ethan{Or parallel rep with efficient ver.}

@@

\Ethan{end of notes}

@@

\Ethan{Take out the following and take from google docs}

Let $L\in\BQP$, and $x\in\set{0,1}^n$.
We start with an overview of the $\QPIP_1$ scheme from \cite{mahadev_delegation}, which was in turn taken from \cite{mf16}.

\begin{protocol}{Verifying yes-instances for $\BQP$}
	\label{proto:BQP}
	We give only a high-level description here.
	\Ethan{Don't say this}
	For more details, see \cref{AlgGroundStateCheck} where we generalize this for $\SampBQP$.
	\Ethan{Reference something else; referencing $\SampBQP$ is a bad idea here}
	\begin{enumerate}
	    \Ethan{Phrase like ``for some input x, generate y"}
		\item The verifier chooses some tensor product of $X$ and $Z$ measurements $\Lambda$
		\Ethan{just say there's some certain distribution that $\Lambda$ was sampled from}
		\item The prover sends the verifier some state $\rho\in\cB^{\otimes m}$ qubit-by-qubit. \Ethan{quantify m?}
		\item The verifier measures $\rho$ according to $S$ \Ethan{give measurement outcome notation}
		\item The verifier decides whether to accept based on the measurement results. \Ethan{``Takes measurement outcome and generates acc/rej"}
	\end{enumerate}
\end{protocol}

Differently from \cref{AlgGroundStateCheck}, \cref{proto:BQP} has negligible completeness and soundness, due to parallel repetition.
We denote the honest prover's action in \cref{proto:BQP} as $\cF$.
Now we compile it using $\mathsf{QHE}$ in order to also achieve blindness:

\begin{protocol}{Blind Protocol for $\BQP$}
	\label{proto:BlindBQP}
	\Ethan{Define/quantify $x$ and whatnot}
	Let $d$ be the depth of the circuit corresponding to $\cF$.
	\begin{enumerate}
		\item The verifier chooses $\Lambda$ and computes $\Lambda'$ using \cref{decodeMeasureOrder}
		\Ethan{Reference to particular steps of the last protocol}
		\item The verifier runs $\mathsf{QHE.Keygen}(1^n, 1^d)$ to get $pk, sk, evk$.
		\item The verifier computes $c=\mathsf{QHE.Enc}_{pk}(x)$
		\item The verifier sends $c$ and $evk$ to the prover
		\item The prover computes $\mathsf{QHE.Eval}(\cF, c)$ and sends it to the verifier qubit-by-qubit.
		\item The verifier measures the incoming ciphertext according to $\Lambda'$
		\item The verifier applies $\widehat{\mathsf{QHE.Dec}_{sk}}$ to the measurement results
		\item The verifier decides whether to accept based on \cref{proto:BQP}
	\end{enumerate}
\end{protocol}

@@

\begin{thm}
	\cref{proto:BlindBQP} preserves the completeness and soundness of \cref{proto:BQP}
\end{thm}
\begin{proof}
    \Ethan{Completeness is trivial, but soundness isn't as trivial as this makes it look like}
	Based on the correctness of $\mathsf{QHE}$, any prover strategy in \cref{proto:BlindBQP} has a corresponding strategy in \cref{proto:BQP}.
\end{proof}

\begin{thm}
    \Ethan{Use ``blind", not IND-CPA for protocols}
	\cref{proto:BlindBQP} is IND-CPA secure.
\end{thm}
\begin{proof}
	The only thing the prover sees is $c$ and $evk$, so this follows directly from $\mathsf{QHE}$'s security.
\end{proof}

>>>>

@@

@@

@@

We start with a high-level description of the $\QPIP_1$ scheme from \cite{mahadev_delegation}, which was in turn taken from \cite{mf16}.

\Ethan{below is copied and pasted from google docs and might need a bit of rephrasing}
Thm 8.4 in Urmila's paper gives a one-message $\QPIP_1$ protocol with XZ measurement for deciding BQP language L.
Roughly, on input $x \in\set{0,1}^n$,  P will send a m = poly(n) qubit certificate state $\rho$ to V qubit by qubit.
V will sample a measurement setting $h \in \set{0,1}^m$ according to certain distribution $\pi_x$, and use h to determine how to measure $\rho$.
Specifically, if $h_i = 0$ (resp., 1), then V will measure the i-th qubit using  X (resp., Z) measurement, and verify the measurement outcome.

\begin{protocol}{Verifying yes-instances for $\BQP$}
	\label{proto:BQP}
	Let $L\in\BQP$, and $x\in\set{0,1}^n$. Let $m=\poly(n)$
	\begin{enumerate}
		\item On input $L$ and $x$, the verifier samples $\Lambda$ from a certain distribution $\pi_{L, x}$, where $\Lambda=\Lambda_1\otimes\ldots\otimes\Lambda_m$; each $\Lambda_i$ is single-qubit $X$ or $Z$ measurements.
		\item The verifier sends $x$ to the prover.
		\item The prover applies a certain CPTP $\cF$ on $x$ to generate $\rho\in\cB^{\otimes m}$.
			\Ethan{Now we need to define CPTP in prelim...}
		\item The prover sends $\rho$ to the verifier qubit-by-qubit.
		\item The verifier measures the incoming qubits of $\rho$ according to $\Lambda$ to get $c$.
		\item The verifier runs some $\BPP$ algorithm $\cV$ on input $c$ and outputs either accept or reject.
	\end{enumerate}
\end{protocol}

\Ethan{below is copied from google docs and need rephrasing}

compile this protocol using QFHE to obtain a blind one message $\QPIP_1$ protocol for BQP with XZ measurement.
High level idea:  run the protocol under Urmila’s QFHE. Namely, $\tilde{V}$ sends $ct = Enc(x)$ to $\tilde{P}$, then $\tilde{P}$ homomorphically evaluate $P_1$ on ct to produce $\tilde{rho} = Enc(\rho)$ and send the encrypted certificate state to $\tilde{V}$.
Discussion: Now $\tilde{V}$ need to obtain the measurement outcome w from the encrypted state $\tilde{rho}$ using qubit-by-qubit XZ measurements. This may not be possible in general. 
Key observation: Our key observation is that Urmila’s QFHE scheme allows this. 
Explain why: Urmila’s QFHE ciphertext has the form of  QOTP on quantum msg + classical FHE ciphertext. So $\tilde{V}$ can do blah blah XZ measurement on $\tilde{rho}$, and recover w from the measurement outcome. We state this as the following fact/key observation: ...

\cref{proto:BQP} has negligible completeness and soundness.
Now we compile it using $\mathsf{QHE}$ in order to also achieve blindness:

\begin{protocol}{Blind Protocol for $\BQP$}
	\label{proto:BlindBQP}
	\Ethan{Define/quantify $x$ and whatnot}
	Let $d$ be the depth of the circuit corresponding to $\cF$.
	Take $\pi_{L, x}$, $\cF$, and $\cV$ to be the same as in \cref{proto:BQP}
	\begin{enumerate}
		\item The verifier samples $\Lambda$ from $\pi_{L, x}$
		\item The verifier computes $\Lambda'$ using \cref{decodeMeasureOrder}
		\item The verifier runs $\mathsf{QHE.Keygen}(1^n, 1^d)$ to get $pk, sk, evk$.
		\item The verifier computes $c=\mathsf{QHE.Enc}_{pk}(x)$
		\item The verifier sends $c$ and $evk$ to the prover
		\item The prover computes $\sigma=\mathsf{QHE.Eval}(\cF, c)$
		\item The prover sends $\sigma$ to the verifier qubit-by-qubit.
		\item The verifier measures the incoming ciphertext according to $\Lambda'$, getting $ct$
		\item The verifier applies $\widehat{\mathsf{QHE.Dec}_{sk}}$ to $ct$, getting $c$.
		\item The verifier applies $\cV$ to $c$ and outputs its result.
	\end{enumerate}
\end{protocol}

@@

\begin{thm}
	\cref{proto:BlindBQP} has negligible completeness and soundness.
\end{thm}
\begin{proof}
    \Ethan{Completeness is trivial, but soundness isn't as trivial as this makes it look like}
	Based on the correctness of $\mathsf{QHE}$, any prover strategy in \cref{proto:BlindBQP} has a corresponding strategy in \cref{proto:BQP}.
\end{proof}

\begin{thm}
	\cref{proto:BlindBQP} is blind.
\end{thm}
\begin{proof}
	The only thing the prover sees is $c$ and $evk$, so this follows directly from $\mathsf{QHE}$'s security.
\end{proof}
